---
title: "Figures from ICML Version of Paper"
output: pdf_document
---

The code in this document creates the plots in the text of the ArXiv version of the paper (as of March 2023) using the saved power computations in the `figures` folder.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 8, fig.height = 1.75)
library(readr)
library(tidyverse)
library(ggthemes)
library(purrr)

plot_colors <- c("#F8766D", # Public Test
                 "#B79F00", # Canonne et al. (CKMUZ)
                 "#00BA38", # Pena-Barrientos (PB)
                 "#00BFC4", # Swanberg et al. (SGGRGB)
                 "#619CFF", # Test of Tests (ToT)/ Awan and Slavkovic (AS)
                 "#F564E3") # Couch et al. (CKSBG)
```

The following creates Figure 2 comparing ToT to PB.

```{r, fig.height = 3}
Figure_2 <- read_csv("figures_data/Figure_2.csv", show_col_types = FALSE)

Figure_2 %>%
  # Adjust Order of Tests in Legend
  mutate(test = factor(test, levels = c("Public Test", "ToT", "PB"))) %>%
  # Create a Variable of Facet Labels
  mutate(eff = paste0("mu*' = ", eff,", '*epsilon*' = ", eps,"'")) %>%
  ggplot(aes(x = n, y = power, color = test)) +
  geom_line(linewidth =  1) +
  facet_grid(rows = vars(eff), labeller = label_parsed) +
  scale_color_manual(values = plot_colors[c(1,5,3)]) +
  labs(x = "Total Sample Size, n", y = "Power", color = "") +
  theme_tufte() +
  theme(legend.position="bottom", legend.margin=margin(-10,0,0,-20))

ggsave("ICML_plots/Fig2.png", width = 3.25, height = 4, 
       dpi=600, units = "in")
```

The following creates Figure 3 comparing ToT to CKMUZ.

```{r, fig.height = 3}
Figure_3 <- read_csv("figures_data/Figure_3.csv", show_col_types = FALSE)

Figure_3 %>%
  # Adjust Order of Tests in Legend
  mutate(test = factor(test, levels = c("Public Test", "ToT", "CKMUZ"))) %>%
  # Create a Variable of Facet Labels
  mutate(eff = case_when(eff == 0.5 ~ "mu*' = 0.5 in one dim.'",
                         eff == 0.1 ~ "mu*' = 0.1 in all dim.'")) %>%
  ggplot(aes(x = n, y = power, color = test)) + 
  geom_line(linewidth =  1) + 
  facet_grid(rows = vars(eff), labeller = label_parsed) +
  labs(x = "Total Sample Size, n", y = "Power", color = "") +
  scale_x_log10() + theme_tufte() +
  scale_color_manual(values = plot_colors[c(1,5,2)]) + 
  theme(legend.position="bottom", legend.margin=margin(0,0,0,-20),
        plot.margin=grid::unit(c(0,0,0,0), "mm"))

ggsave("ICML_plots/Fig3.png", width = 3.25, height = 4, 
       dpi=600, units = "in")
```

The following creates Figure 4 comparing ToT to CKSBG and SGGRGB.

```{r}
Figure_4 <- read_csv("figures_data/Figure_4.csv", show_col_types = FALSE)

Figure_4 %>%
  # Adjust Order of Tests in Legend
  mutate(test = factor(test, levels = c("Public Test", "ToT",
                                        "CKSBG", "SGGRGB"))) %>%
  ggplot(aes(x = n, y = power, color = test)) + geom_line(linewidth =  1) +
  labs(x = "Total Sample Size, n", y = "Power", color = "") + 
  scale_x_log10() + theme_tufte() +
  scale_color_manual(values = plot_colors[c(1,5,6,4)]) + 
  theme(legend.position="bottom", legend.margin=margin(0,0,0,-20),
      plot.margin=grid::unit(c(0,0,0,0), "mm")) +
  guides(color=guide_legend(nrow=2, byrow=TRUE))

ggsave("ICML_plots/Fig4.png", width = 3.25, height = 2.75,
       dpi=600, units = "in")
```

The following creates Figure 5 in the appendix comparing AS to PB.

```{r, fig.height = 3}
Figure_5 <- read_csv("figures_data/Figure_5.csv", show_col_types = FALSE)

Figure_5 %>%
  mutate(epsilon = paste0("epsilon*' = ", eps,"'")) %>%
  mutate(test = case_when(test == "Awan & Slavkovic" ~ "AS", 
                          test == "Pena & Barrientos" ~ "PB")) %>%
  ggplot(aes(x = theta, y = power, color = test)) +
  geom_line(linewidth =  1) +
  facet_grid(rows = vars(epsilon), labeller = label_parsed) +
  labs(x = expression("Effect Size, "*theta), color = "", y = "Power") +
  scale_color_manual(values = plot_colors[c(5,3)]) +
  scale_x_continuous(labels = c(0, 0.25, 0.5, 0.75, 1)) +
  theme_tufte()

ggsave("ICML_plots/Fig5.png", width = 6.75, height = 1.75*2,
       dpi=600, units = "in")
```

The following creates Figures 6-7 in the appendix comparing ToT to PB.

```{r}
Figure_6 <- read_csv("figures_data/Figure_6.csv", show_col_types = FALSE)

Figure_6 %>%
  mutate(test = case_when(test == "Public" ~ "Public Test", 
                          test == "PB" ~ "PB",
                          test == "ToT" ~ "ToT")) %>%
  mutate(test = factor(test, levels = c("Public Test", "ToT", "PB"))) %>%
  ggplot(aes(x = n, y = power, color = test)) +
  geom_line(linewidth =  1) +
  scale_color_manual(values = plot_colors[c(1,5,3)]) +
  labs(x = "Total Sample Size, n", y = "Power", color = "") +
  theme_tufte()

ggsave("ICML_plots/Fig6.png", width = 6.75, height = 1.75,
       dpi=600, units = "in")
```

```{r}
Figure_7 <- read_csv("figures_data/Figure_7.csv", show_col_types = FALSE)

Figure_7 %>%
  mutate(test = case_when(test == "Public" ~ "Public Test", 
                          test == "PB" ~ "PB",
                          test == "ToT" ~ "ToT")) %>%
  mutate(test = factor(test, levels = c("Public Test", "ToT", "PB"))) %>%
  ggplot(aes(x = n, y = power, color = test)) +
  geom_line(linewidth =  1) +
  scale_color_manual(values = plot_colors[c(1,5,3)]) +
  labs(x = "Total Sample Size, n", y = "Power", color = "") +
  theme_tufte()

ggsave("ICML_plots/Fig7.png", width = 6.75, height = 1.75,
       dpi=600, units = "in")
```

The following creates Figures 8-12 in the appendix comparing ToT to CKMUZ.

```{r}
Figure_8 <- read_csv("figures_data/Figure_8.csv", show_col_types = FALSE)

Figure_8 %>%
  mutate(test = case_when(test == "Public" ~ "Public Test", 
                          test == "Canonne" ~ "CKMUZ",
                          test == "Test of tests" ~ "ToT")) %>%
  mutate(test = factor(test, levels = c("Public Test", "ToT", "CKMUZ"))) %>%
  ggplot(aes(x = n, y = power, color = test)) + 
  geom_line(linewidth =  1) + 
  labs(x = "Total Sample Size, n", y = "Type I Error", color = "") +
  scale_x_log10() + theme_tufte() + ylim(0,1) + 
  scale_color_manual(values = plot_colors[c(1,5,2)])

ggsave("ICML_plots/Fig8.png", width = 6.75, height = 1.75,
       dpi=600, units = "in")
```

```{r}
Figure_9 <- read_csv("figures_data/Figure_9.csv", show_col_types = FALSE)

Figure_9 %>%
  filter(!(test == "Canonne" & n < 359)) %>%
  mutate(test = case_when(test == "Public" ~ "Public Test", 
                          test == "Canonne" ~ "CKMUZ",
                          test == "Test of tests" ~ "ToT")) %>%
  mutate(test = factor(test, levels = c("Public Test", "ToT", "CKMUZ"))) %>%
  ggplot(aes(x = n, y = power, color = test)) + 
  geom_line(linewidth =  1) + 
  labs(x = "Total Sample Size, n", y = "Power", color = "") +
  scale_x_log10() + theme_tufte() + 
  scale_color_manual(values = plot_colors[c(1,5,2)])

ggsave("ICML_plots/Fig9.png", width = 6.75, height = 1.75,
       dpi=600, units = "in")
```

```{r}
Figure_10 <- read_csv("figures_data/Figure_10.csv", show_col_types = FALSE)

Figure_10 %>%
  filter(!(test == "Canonne" & n < 359)) %>%
  mutate(test = case_when(test == "Public" ~ "Public Test", 
                          test == "Canonne" ~ "CKMUZ",
                          test == "Test of tests" ~ "ToT")) %>%
  mutate(test = factor(test, levels = c("Public Test", "ToT", "CKMUZ"))) %>%
  ggplot(aes(x = n, y = power, color = test)) + 
  geom_line(linewidth =  1) + 
  labs(x = "Total Sample Size, n", y = "Power", color = "") +
  scale_x_log10() + theme_tufte() + 
  scale_color_manual(values = plot_colors[c(1,5,2)])

ggsave("ICML_plots/Fig10.png", width = 6.75, height = 1.75,
       dpi=600, units = "in")
```

```{r}
Figure_11 <- read_csv("figures_data/Figure_11.csv", show_col_types = FALSE)

Figure_11 %>%
  filter(!(test == "Canonne" & n < 359)) %>%
  mutate(test = case_when(test == "Public" ~ "Public Test", 
                          test == "Canonne" ~ "CKMUZ",
                          test == "Test of tests" ~ "ToT")) %>%
  mutate(test = factor(test, levels = c("Public Test", "ToT", "CKMUZ"))) %>%
  ggplot(aes(x = n, y = power, color = test)) + 
  geom_line(linewidth =  1) + 
  labs(x = "Total Sample Size, n", y = "Power", color = "") +
  scale_x_log10() + theme_tufte() + 
  scale_color_manual(values = plot_colors[c(1,5,2)])

ggsave("ICML_plots/Fig11.png", width = 6.75, height = 1.75,
       dpi=600, units = "in")
```

```{r}
Figure_12 <- read_csv("figures_data/Figure_12.csv", show_col_types = FALSE)

Figure_12 %>%
  filter(!(test == "Canonne" & n <= 400)) %>%
  mutate(test = case_when(test == "Public" ~ "Public Test", 
                          test == "Canonne" ~ "CKMUZ",
                          test == "Test of tests" ~ "ToT")) %>%
  mutate(test = factor(test, levels = c("Public Test", "ToT", "CKMUZ"))) %>%
  ggplot(aes(x = n, y = power, color = test)) + 
  geom_line(linewidth =  1) + 
  labs(x = "Total Sample Size, n", y = "Power", color = "") +
  scale_x_log10() + theme_tufte() + 
  scale_color_manual(values = plot_colors[c(1,5,2)])

ggsave("ICML_plots/Fig12.png", width = 6.75, height = 1.75,
       dpi=600, units = "in")
```

```{r}
Figure_13 <- read_csv("figures_data/Figure_13.csv", show_col_types = FALSE)

Figure_13 %>%
  filter(eps == 1, n <= 1226) %>%
  filter(test %in% c("Public ANOVA", "kw abs", "Private ANOVA",
                     "Test of tests")) %>%
  mutate(test = case_when(test == "Public ANOVA" ~ "Public Test", 
                          test == "Private ANOVA" ~ "SGGRGB",
                          test == "kw abs" ~ "CKSBG",
                          test == "Test of tests" ~ "ToT")) %>%
  mutate(test = factor(test, levels = c("Public Test", "ToT",
                                        "CKSBG", "SGGRGB"))) %>%
  ggplot(aes(x = n, y = power, color = test)) + geom_line(linewidth =  1) +
  labs(x = "Total Sample Size, n", y = "Power", color = "") + 
  scale_x_log10() + theme_tufte() +
  scale_color_manual(values = plot_colors[c(1,5,6,4)])

ggsave("ICML_plots/Fig13.png", width = 6.75, height = 1.75,
       dpi=600, units = "in")
```

```{r}
Figure_14 <- read_csv("figures_data/Figure_14.csv", show_col_types = FALSE)

Figure_14 %>%
  filter(n <= 1226) %>%
  filter(test %in% c("pub", "Private KW", "Private ANOVA",
                     "Test of tests")) %>%
  mutate(test = case_when(test == "pub" ~ "Public Test", 
                          test == "Private ANOVA" ~ "SGGRGB",
                          test == "Private KW" ~ "CKSBG",
                          test == "Test of tests" ~ "ToT")) %>%
  mutate(test = factor(test, levels = c("Public Test", "ToT",
                                        "CKSBG", "SGGRGB"))) %>%
  ggplot(aes(x = n, y = power, color = test)) + geom_line(linewidth =  1) +
  labs(x = "Total Sample Size, n", y = "Power", color = "") + 
  scale_x_log10() + theme_tufte() +
  scale_color_manual(values = plot_colors[c(1,5,6,4)])

ggsave("ICML_plots/Fig14.png", width = 6.75, height = 1.75,
       dpi=600, units = "in")
```

```{r}
Figure_15 <- read_csv("figures_data/Figure_15.csv", show_col_types = FALSE)

Figure_15 %>%
  filter(n <= 1226) %>%
  filter(test %in% c("pub", "Private KW", "Private ANOVA",
                     "Test of tests")) %>%
  mutate(test = case_when(test == "pub" ~ "Public Test", 
                          test == "Private ANOVA" ~ "SGGRGB",
                          test == "Private KW" ~ "CKSBG",
                          test == "Test of tests" ~ "ToT")) %>%
  mutate(test = factor(test, levels = c("Public Test", "ToT",
                                        "CKSBG", "SGGRGB"))) %>%
  ggplot(aes(x = n, y = power, color = test)) + geom_line(linewidth =  1) +
  labs(x = "Total Sample Size, n", y = "Power", color = "") + 
  scale_x_log10() + theme_tufte() +
  scale_color_manual(values = plot_colors[c(1,5,6,4)])

ggsave("ICML_plots/Fig15.png", width = 6.75, height = 1.75,
       dpi=600, units = "in")
```

```{r}
Figure_16 <- read_csv("figures_data/Figure_16.csv", show_col_types = FALSE)

Figure_16 %>%
  filter(n <= 1311) %>%
  filter(test %in% c("Public KW", "New KW", "Private ANOVA",
                     "Test of tests")) %>%
  mutate(test = case_when(test == "Public KW" ~ "Public Test", 
                          test == "Private ANOVA" ~ "SGGRGB",
                          test == "New KW" ~ "CKSBG",
                          test == "Test of tests" ~ "ToT")) %>%
  mutate(test = factor(test, levels = c("Public Test", "ToT",
                                        "CKSBG", "SGGRGB"))) %>%
  ggplot(aes(x = n, y = power, color = test)) + geom_line(linewidth =  1) +
  labs(x = "Total Sample Size, n", y = "Power", color = "") + 
  scale_x_log10() + theme_tufte() +
  scale_color_manual(values = plot_colors[c(1,5,6,4)])

ggsave("ICML_plots/Fig16.png", width = 6.75, height = 1.75,
       dpi=600, units = "in")
```